Using Refactoring Techniques to Reduce Duplication in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-04-23 sattose/paper.tex
Made a start with the background

\subsection{Background}
%TODO: What are clone classes, what are clone instances, etc.

>>>>

\subsection{Background}
As code clones are seen as one of the most harmful types of technical debt, they have been studied very extensively. A survey by Roy et al \cite{roy2007survey} states definitions for various important concepts in code clone research. In this survey he mentions the concept ``clone pair'', which is \textit{a set of two code portions/fragments which are identical or similar to each other}. Furthermore, he defined ``clone class'' as \textit{the union of all clone pairs}. Apart from this, we use the definition ``clone instance'', which is a single code portion/fragment that is part of either a clone pair or clone class.

There are already a few researches that look into refactoring opportunities for clone pairs \cite{}
%TODO: What are clone classes, what are clone instances, etc.
